Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-05-30 SDSS Presentation/SDSS Presentation.Rmd
styling updates

---
title: "Exploring Rural Shrink Smart Through Guided Discovery Dashboards"
author: "Denise R. Bradford and Susan R. Vanderplas, PhD"
date: "June 8, 2022"
output:
  xaringan::moon_reader:
    css: ["default", "unl.css"]
    lib_dir: libs
    includes:
      in_header: header.html
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

class:inverse
## About Me

- PhD student in Statistics at University of Nebraska - Lincoln
- MS/BS in Applied Statistics from Purdue University

- Research Areas
  - Data Science - automation, data pipelines, tools
  - Visualization - perception, design, and implementation
  - Sports Analytics - deploying useful statistical methods for sports-related problems
---

@@

- There are objective measures of things that contribute to QOL available in public datasets
.small.emph[
- School ratings
- Town budgets for services
- Access to medical care, shopping, etc.
- Transportation trends
- Demographic shifts
- City level cooperative agreements with other government entities and NGOs
]

@@

- .red[Project Question:] How do we leverage .emph.cerulean[data science] and .emph.cerulean[survey design] to reduce the length of the survey and maintain reliability?
    - Can objective measures of QOL contributors be incorporated into the survey design?
    - Can we focus on estimating only things that objective measurements don't capture?

@@

- Assess correlation between public data and Iowa Small Town Poll QOL estimates on different dimensions

- .emph.cerulean[Survey Stats problems]: 
    - Incorporate this information into survey designs
    - Change up design of the survey to split questions across participants, etc.

>>>>

---
title: "Exploring Rural Shrink Smart Through Guided Discovery Dashboards"
author: "Denise R. Bradford and Susan R. Vanderplas, PhD"
date: "June 8, 2022"
output:
  xaringan::moon_reader:
    seal: false
    includes:
      after_body:
        "js-addins.html"
    mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-MML-AM_HTMLorMML"
    css: ["default", "metropolis-fonts", "metropolis" ,"css/modal.css", "css/sizeformat.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightlines: true
      countIncrementalSlides: true
---
class:title-slide-custom

```{r, child = "style.Rmd"}
```

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
# Packages
library(emoji)
library(purrr)
library(tidyverse)
library(gridExtra)
library(nullabor)
library(scales)
library(knitr)
library(kableExtra)
library(RefManageR)
library(iconr)
library(fontawesome)
# download_fontawesome()

# References
bib <- ReadBib("bib/references.bib", check = FALSE)
ui <- "- "

# R markdown options
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      cache = FALSE,
                      dpi = 300)
options(htmltools.dir.version = FALSE)
options(knitr.kable.NA = '')
```

```{r, include = F, eval = T, cache = F}
clean_file_name <- function(x) {
  basename(x) %>% str_remove("\\..*?$") %>% str_remove_all("[^[A-z0-9_]]")
}
img_modal <- function(src, alt = "", id = clean_file_name(src), other = "") {

  other_arg <- paste0("'", as.character(other), "'") %>%
    paste(names(other), ., sep = "=") %>%
    paste(collapse = " ")

  js <- glue::glue("<script>
        /* Get the modal*/
          var modal{id} = document.getElementById('modal{id}');
        /* Get the image and insert it inside the modal - use its 'alt' text as a caption*/
          var img{id} = document.getElementById('img{id}');
          var modalImg{id} = document.getElementById('imgmodal{id}');
          var captionText{id} = document.getElementById('caption{id}');
          img{id}.onclick = function(){{
            modal{id}.style.display = 'block';
            modalImg{id}.src = this.src;
            captionText{id}.innerHTML = this.alt;
          }}
          /* When the user clicks on the modalImg, close it*/
          modalImg{id}.onclick = function() {{
            modal{id}.style.display = 'none';
          }}
</script>")

  html <- glue::glue(
     " <!-- Trigger the Modal -->
<img id='img{id}' src='{src}' alt='{alt}' {other_arg}>
<!-- The Modal -->
<div id='modal{id}' class='modal'>
  <!-- Modal Content (The Image) -->
  <img class='modal-content' id='imgmodal{id}'>
  <!-- Modal Caption (Image Text) -->
  <div id='caption{id}' class='modal-caption'></div>
</div>
"
  )
  write(js, file = "js-addins.html", append = T)
  return(html)
}
# Clean the file out at the start of the compilation
write("", file = "js-addins.html")
```

<br><br>
# Exploring Rural Shrink Smart Through Guided Discovery Dashboards
## SDSS 2022
### June 8, 2022
#### Denise Bradford
#### Department of Statistics, University of Nebraska - Lincoln 
##### `r fa("envelope", fill = "black")` [denise.bradford@huskers.unl.edu](denise.bradford@huskers.unl.edu) 
##### `r fa("home", fill = "black")` [www.deniserbradford.com](https://www.deniserbradford.com/) 
##### `r fa("github", fill = "black")` [drbradford12](https://github.com/drbradford12)

???
Thank you for inviting me for a visit today and for attending my talk.

---
class:primary
# Outline

+ Introduction to Rural Shrink Smart Project with Iowa State

+ Why Dashboards?

+ Dashboard Design and Guided Discovery Learning (GDL)

+ Parallel Coordinate Plots (PCPs) and the naive user

+ Data Collection and Feedback the loop

+ Future Work

???
In this talk today, I will provide a background of the Rural Shrink Smart Project. I will then provide a framework to way using a dashboard can be helpful to these population discovery of gaining insights from other towns. I will continue to discuss the usefulness of parallel coordinate plots on the naive user. I will conclude with future work.

---

@@

- There are objective measures of things that contribute to QOL available in public datasets
.medium.emph[
- School ratings
- Town budgets for services
- Access to medical care, shopping, etc.
- Transportation trends
- Demographic shifts
- City level cooperative agreements with other government entities and NGOs
]

@@

- .red[Project Question:] How do we leverage .emph.cerulean[data science] and .emph.cerulean[exploratory data methods] to inform town leaders to reduce the shrinkage and maintain reliability?
    - Can traditional dashboard design of open source data be incorporated into overall decision-making?
    - Can we focus on estimating only things that objective measurements don't capture?

@@

- Assess usability, intelligibility and adaptability to new statistical methodology.

- .emph.cerulean[Exploratory Data Analysis (EDA)]: 
    - Incorporate this information into an exploratory dashboard
    - Change up design of the dashboard to manage the easy of adaptability across our rural towns
